\bibitem{bib:mobile-challenge} Mizouni, R.; Serhani, A. ; Dssouli, R. ; Benharref, A.: Back to Results Challenges in “mobilizing” desktop applications: a new methodology for requirements engineering,  Coll. of Inf. Technol., UAE Univ., Al-Ain, United Arab Emirates, 2009

\bibitem{bib:mobile-paradigm} Ngu Phuc Huy; Do Van Thanh: Selecting the right mobile app paradigms Dept. of Telematics, Norwegian Univ. of Sci. \& Technol., Trondheim, Norway, 2012

\bibitem{bib:iot-middleware}Razzaque, M.A.; Milojevic-Jevric, M. ; Palade, A. ; Clarke, S.: Middleware for Internet of Things: a Survey,  Trinity College Dublin, Dublin, Ireland.

\bibitem{bib:mgr-rpi} Chi Winth Ea; Morten Sørbø: Multi-purpose Embedded Communication Gateway: System Design and Testbed Implementation, University of Agder, 2014

\bibitem{bib:xhr} Adeyeye, M.; Makitla, I. ; Fogwill, T.: Determining the signalling overhead of two common WebRTC methods: JSON via XMLHttpRequest and SIP over WebSocket, Dept. of Inf. Technol., Cape Peninsula Univ. of Technol., Cape Town, South Africa, 2013

\bibitem{bib:ruby-doc} Dokumentacja języka Ruby, \url{https://www.ruby-lang.org/en/}

\bibitem{bib:rails-doc} Dokumentacja Ruby on rails, \url{http://guides.rubyonrails.org/}

\bibitem{bib:coffeescript-doc} Dokumentacja CoffeeScript, \url{http://coffeescript.org/}

\bibitem{bib:sass-doc} Dokumentacja Sass, \url{http://sass-lang.com/}

\bibitem{bib:jquery-doc} Dokumentacja biblioteki jQuery, \url{https://jquery.com/}

\bibitem{bib:rvm-install} Opis instalacji RVM (Ruby Version Manager), \url{https://rvm.io/rvm/install }
